Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-10-24 Thesis/chapter/05-computational-details.tex
ueberarbeitet
include gen figures

\subsection{Data Processing}
\label{sec:eval}
%\td{describe problem and solution found}
For every sample multiple \gls{iv} curves were measured. 
The main difficulty faced in processing the data was to present the measurements obtain 
from a sample in one representative number. 
The average of each conductance would be an obvious choice but difficult to represent a 
sample correctly since the possible values of conductance span accross several magnitudes.
So the average of logarithms of conductances is the next nearby ansatz.
\todo{why didn't i just take this?}
\td{L2 norm because it might be easier to compare to other methods. }
\td{inspired by euclidean norm/L2 distance from ideal case} 
\td{wanted to put more weight on bad shunts}
\td{plot avg, avg(log), avg(log-13)}

@@

%\subsection{EMMA Propagation}
\begin{table}[htb]
	\centering
	\begin{tabular}{ccccccc}
		\hline
		\hline
conc	&layers	&vDOC	&TDOC	&vCal	&Tcal	&	\\
		\hline
1	&10	&5	&20	&120	&400	&\\
1	&4	&0.1	&20	&120	&500	&\\
5	&10	&0.1	&20	&120	&500	&\\
5	&4	&5	&20	&480	&400	&\\
1	&5	&5	&80	&120	&500	&\\
1	&10	&1	&80	&480	&400	&\\
5	&5	&1	&80	&120	&400	&\\
5	&10	&5	&80	&480	&500	&\\
2	&8	&0.5	&40	&360	&470	&\\
2	&6	&2	&40	&360	&430	&\\
		\hline
%4	&12	&-	&-	&-	&-&\\
1	&4	&12	&70	&120	&500	&\\
1	&9	&18	&80	&240	&400	&\\
%2	&5	&18	&70	&-	&-		&\\
4	&6	&14	&60	&240	&500	&\\
4	&6	&14	&60	&240	&500	&\\
4	&6	&14	&60	&240	&500	&\\
		\hline
2	&10	&20	&40	&120	&500	&6113\\
3	&8	&18	&70	&1080	&300	&2850\\
3	&6	&10	&50	&1080	&400	&5526	\\
%3	&10	&14	&50	&600	&500	&-7374	\\
3	&10	&16	&80	&120	&500	&6554	\\
4	&6	&16	&80	&1080	&300	&2947	\\
3	&12	&12	&80	&840	&500	&8318	\\
3	&10	&14	&50	&600	&500	&7374	\\
5	&6	&10	&60	&1080	&400	&5648	\\
5	&10	&20	&60	&360	&300	&3956	\\
5	&12	&14	&60	&1080	&300	&2700	\\
		\hline
%2	&2	&10	&40	&600	&300	&-7201	\\
2	&4	&10	&80	&1080	&300	&6101	\\
%2	&4	&10	&40	&600	&300	&-7201	\\
2	&4	&10	&40	&600	&300	&7201	\\
3	&4	&12	&60	&600	&300	&1462	\\
4	&4	&10	&80	&1080	&300	&2883	\\
5	&12	&20	&70	&600	&300	&1680	\\
		\hline
2	&4	&10	&40	&120	&300	&1	\\
2	&4	&10	&40	&120	&500	&6001	\\
3	&4	&10	&40	&120	&500	&6102	\\
5	&4	&10	&80	&1080	&300	&2884	\\
5	&12	&20	&60	&120	&300	&360	\\
		\hline
3	&4	&10	&40	&600	&400	&4202	\\
2	&6	&20	&40	&120	&500	&6105	\\
%4	&4	&14	&80	&1080	&300	&-2923	\\
5	&12	&14	&60	&600	&300	&1500	\\
3	&6	&14	&60	&600	&300	&1486	\\
4	&4	&14	&80	&1080	&300	&2923	\\
		\hline
4	&8	&18	&80	&1080	&300	&2971	\\
3	&8	&10	&50	&1080	&300	&2530	\\
2	&12	&16	&40	&120	&400	&3077	\\
2	&10	&18	&60	&1080	&300	&2733	\\
4	&10	&10	&50	&1080	&300	&2535	\\
		\hline
		\hline
	\end{tabular}
	\caption{}
	\label{tab:emma}
\end{table}

>>>>

\subsection{Data Processing}
\label{sec:eval}
Reading list
\begin{itemize}
    %\item https://de.wikipedia.org/wiki/Globaler_F-Test
    %\item https://de.wikipedia.org/wiki/Optimale_Versuchsplanung
    %\item Curse of dimensionality scholar
    %\item linear regression von ungar 
    %\item ridge regression + support vector machine
    %\item correlation vs covariance
    %\item https://en.wikipedia.org/wiki/Regression_analysis
    %\item https://en.wikipedia.org/wiki/Noise_reduction
    %\item https://en.wikipedia.org/wiki/Feature_extraction
    %\item https://en.wikipedia.org/wiki/Feature_selection
    %\item https://en.wikipedia.org/wiki/Dimensionality_reduction
    %\item file:///home/pur/Doc/Uni/Chemie_Master/Int_AIT/Int.git/Code/ML/98_things_can_go_wrong_in_ML_project.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.PCA.html
    %\item https://scikit-learn.org/stable/modules/generated/sklearn.decomposition.KernelPCA.html#sklearn.decomposition.KernelPCA
    \item 
    \item 
    \item 
\end{itemize}
%\td{describe problem and solution found}
For every sample multiple \gls{iv} curves were measured. 
The main difficulty faced in processing the data was to present the measurements obtain 
from a sample in one representative number. 
The average of each conductance would be an obvious choice but difficult to represent a 
sample correctly since the possible values of conductance span accross several magnitudes.
So the average of logarithms of conductances is the next nearby ansatz.
\todo{why didn't i just take this?}
\td{L2 norm because it might be easier to compare to other methods. }
\td{inspired by euclidean norm/L2 distance from ideal case} 
\td{wanted to put more weight on bad shunts}
\td{plot avg, avg(log), avg(log-13)}

@@

\td{system behavior are discussed in Modeling the Results.
Algorithm and Coating Features. The theoretical efficiency
of the proposed approach has been verified using a simulation
based on a preliminary experimental model (48 recipes evalu-
ated, see the Supporting Information, S3). Then, 15 new experi-
ments were selected for each subsequent time instant. Each time
instant involves experiment identification, solution preparation,
coating deposition, and spot analysis.
Figure 2a presents the laser scanner measurement of a spot
}\cite{Carta2011}
%\subsection{EMMA Propagation}
%\begin{table}[htb]
%	\centering
%	\begin{tabular}{ccccccc}
%		\hline
%		\hline
%conc	&layers	&vDOC	&TDOC	&vCal	&Tcal	&	\\
%		\hline
%1	&10	&5	&20	&120	&400	&\\
%1	&4	&0.1	&20	&120	&500	&\\
%5	&10	&0.1	&20	&120	&500	&\\
%5	&4	&5	&20	&480	&400	&\\
%1	&5	&5	&80	&120	&500	&\\
%1	&10	&1	&80	&480	&400	&\\
%5	&5	&1	&80	&120	&400	&\\
%5	&10	&5	&80	&480	&500	&\\
%2	&8	&0.5	&40	&360	&470	&\\
%2	&6	&2	&40	&360	&430	&\\
%		\hline
%%4	&12	&-	&-	&-	&-&\\
%1	&4	&12	&70	&120	&500	&\\
%1	&9	&18	&80	&240	&400	&\\
%%2	&5	&18	&70	&-	&-		&\\
%4	&6	&14	&60	&240	&500	&\\
%4	&6	&14	&60	&240	&500	&\\
%4	&6	&14	&60	&240	&500	&\\
%		\hline
%2	&10	&20	&40	&120	&500	&6113\\
%3	&8	&18	&70	&1080	&300	&2850\\
%3	&6	&10	&50	&1080	&400	&5526	\\
%%3	&10	&14	&50	&600	&500	&-7374	\\
%3	&10	&16	&80	&120	&500	&6554	\\
%4	&6	&16	&80	&1080	&300	&2947	\\
%3	&12	&12	&80	&840	&500	&8318	\\
%3	&10	&14	&50	&600	&500	&7374	\\
%5	&6	&10	&60	&1080	&400	&5648	\\
%5	&10	&20	&60	&360	&300	&3956	\\
%5	&12	&14	&60	&1080	&300	&2700	\\
%		\hline
%%2	&2	&10	&40	&600	&300	&-7201	\\
%2	&4	&10	&80	&1080	&300	&6101	\\
%%2	&4	&10	&40	&600	&300	&-7201	\\
%2	&4	&10	&40	&600	&300	&7201	\\
%3	&4	&12	&60	&600	&300	&1462	\\
%4	&4	&10	&80	&1080	&300	&2883	\\
%5	&12	&20	&70	&600	&300	&1680	\\
%		\hline
%2	&4	&10	&40	&120	&300	&1	\\
%2	&4	&10	&40	&120	&500	&6001	\\
%3	&4	&10	&40	&120	&500	&6102	\\
%5	&4	&10	&80	&1080	&300	&2884	\\
%5	&12	&20	&60	&120	&300	&360	\\
%		\hline
%3	&4	&10	&40	&600	&400	&4202	\\
%2	&6	&20	&40	&120	&500	&6105	\\
%%4	&4	&14	&80	&1080	&300	&-2923	\\
%5	&12	&14	&60	&600	&300	&1500	\\
%3	&6	&14	&60	&600	&300	&1486	\\
%4	&4	&14	&80	&1080	&300	&2923	\\
%		\hline
%4	&8	&18	&80	&1080	&300	&2971	\\
%3	&8	&10	&50	&1080	&300	&2530	\\
%2	&12	&16	&40	&120	&400	&3077	\\
%2	&10	&18	&60	&1080	&300	&2733	\\
%4	&10	&10	&50	&1080	&300	&2535	\\
%		\hline
%		\hline
%	\end{tabular}
%	\caption{}
%	\label{tab:emma}
%\end{table}
%

### 2022-10-24 Thesis/chapter/060-results-material.tex
include gen figures

The \gls{sem} pictures were not easy to take since we were trying to create an insulator 
and the quality of the picture relies on the conductance of the material's surface. 
This means that the better the quality of the resulting layer the more tedious it was to get/take a decent SEM image. 
Figure \ref{fig:sem-old} shows ausschnitte of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
Large cracks and inhomogenity were part of (ausmachen) all samples created with the Anwar recipe; 
also/even after several/multiple/various alteration to the recipe.

@@

%\td{instead of changing the stabilisation agent before optimisation, could change after pso, was vor und nachteile?}
after realizing the improved effectiveness of \gls{ipo} for experimentation, 
it was decided that EMMA will be executed with \gls{ipo} solution.
\begin{figure}
    \centering
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/iv-199-acoh.png}
        \caption{iv acoh} \label{fig:iv-acoh}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/iv-201-acoh-ipo.png}
        \caption{iv acoh ipo} \label{fig:iv-acoh-ipo}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/iv-192-ipo.png}
        \caption{ipo} \label{fig:ipo}
    \end{subfigure}
    \caption{iv of 6x4F} \label{fig:iv}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{V-I}
\begin{figure}
    \centering
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-146-good-10x1F.png}
        \caption{log} \label{fig:log1}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-154-okay-3x4F.png}
        \caption{log} \label{fig:log2}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
        \caption{log} \label{fig:log3}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
        \caption{stat} \label{fig:stat1}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
        \caption{stat} \label{fig:stat2}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
        \caption{stat} \label{fig:stat3}
    \end{subfigure}
    \caption{maybe remove 146 and make 154 good AND set yrange [E-1:E-14]} \label{fig:iv}
\end{figure}

>>>>

The \gls{sem} pictures were not easy to take since we were trying to create an insulator 
and the quality of the picture relies on the conductance of the material's surface. 
This means that the better the quality of the resulting layer the more tedious it was to get/take a decent SEM image. 
Figures \ref{fig:sem-old1} and \ref{fig:sem-old2} shows ausschnitte of \gls{zro} (dark) on top of \gls{fto} (finely polycrystalline). 
These were the results of a single (figure \ref{fig:sem-old1}) and double (figure \ref{fig:sem-old2}) "layer" of the aquatic recipe. 
Large cracks and inhomogenity were part of (ausmachen) all samples created with the Anwar recipe; 
also/even after several/multiple/various alteration to the recipe.

@@

%\td{instead of changing the stabilisation agent before optimisation, could change after pso, was vor und nachteile?}
after realizing the improved effectiveness of \gls{ipo} for experimentation, 
it was decided that EMMA will be executed with \gls{ipo} solution.
\begin{figure}
    \centering
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/iv-199-acoh.png}
        \caption{iv acoh} \label{fig:iv-acoh}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/iv-201-acoh-ipo.png}
        \caption{iv acoh ipo} \label{fig:iv-acoh-ipo}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/iv-192-ipo.png}
        \caption{ipo} \label{fig:ipo}
    \end{subfigure}
    \caption{iv of 6x4F} \label{fig:iv-ipo}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{V-I}
\begin{figure}
    \centering
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-154-good-3x4F.png}
        \caption{log good 3x4F} \label{fig:log2}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-146-okay-10x1F.png}
        \caption{log okay 10x1F} \label{fig:log1}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/log-156-bad-3x3F.png}
        \caption{log bad 3x3F} \label{fig:log3}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-154-okay-3x4F.png}
        \caption{stat good 3x4F} \label{fig:stat2}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-146-good-10x1F.png}
        \caption{stat okay 10x1F} \label{fig:stat1}
    \end{subfigure}
    \begin{subfigure}{.3\textwidth}
        \includegraphics[width=\textwidth]{Pics/iv/stat-156-bad-3x3F.png}
        \caption{stat bad 3x3F} \label{fig:stat3}
    \end{subfigure}
    \caption{maybe remove 146 and make 154 good AND set yrange [E-1:E-14] and show phd threshold} \label{fig:iv}
\end{figure}

### 2022-10-24 Thesis/chapter/061-results-emma.tex
include gen figures

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{EMMA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{what is best}
\begin{align}
%    G    & = -3.7 + 0.18 * TCal +  8.1 * max(0,6-layr)\\
%    \rho & = -0.78 + 0.0024 * TCal + 0.13 * max(0,6-layr)
    G &=      -19 + 0.28 * TCal  - 0.022 * layr*TCal  +  0.16 * h(layr-6)*TDOC \\
    \rho &=  -0.87 + 0.0047 * TCal  - 0.00036 * layr*TCal  +  0.0024 * h(layr-6)*TDOC \\
    \lambda &=  6.8 - 0.014 * TCal  + 0.0018 * layr*TCal  + 0.0060 * h(layr-6)*TDOC \\
    v_{cal} &= 29 - 0.052 * TCal  + 0.0011 * layr*TCal  -  0.011 * h(layr-6)*TDOC 
    \label{eq:emma}
\end{align}
what was the best result? For each particle there is best and global best. 
https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation

@@

\begin{table}[h]
	\centering
    \caption{Global best per generation}
	\label{tab:emma_gen}
	\begin{tabular}{cccccccc}
        \hline\hline
    generation  &enr &conc &layr &vDOC &TDOC &vCal &TCal\\
        \hline
     1   &1       &2    &4   &10   &40  &120  &300\\
     2   &5       &2    &6   &10   &40  &120  &300\\
     3   &2947    &4    &6   &16   &80 &1080  &300\\
     4   &2405    &2    &6   &10   &40 &1080  &300\\
     5   &13      &2   &10   &10   &40  &120  &300\\
    \hline\hline
	\end{tabular}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=.6\textwidth]{Pics/stats/G-t.png}
    \caption{conductivity G [a.u.] against sample number (is this even correct?)}
    \label{fig:G-t}
\end{figure}

\td{TODO: check if the sorted correctly? Make generation graph with boxplot }
    \td{TODO: visualize} how the population moved across the space (with parallel coordinates? or see page 121)
        \url{https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{analyse data with other methods post optimization}
Anova shows that the influence of TCal is significant as shown by the F 
\begin{itemize}
    \item ANOVA (influence of TCal) \texttt{Code/Statistics/sub/anova.R}
    \item lin regression (influence of conc) \texttt{Code/Statistics/sub/linreg.py}
    \item grid search 
    \item KRR (???)
    \item SVM (???)
\end{itemize}

and cite something pro forma \cite{ncbi1butanol}
\td{plot the predicted data for variables which should be excluded (Tcal, Vcal,Conc, layers)}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{EMMA}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{all samples}
%\input{chapter/emma.table.tex}
A total of 30 recipes have been investigated in 
five iterations of the algorithm ($t = 0, \dots,4$). 
%The best recipe identified by the EMMA algorithm is as follows: 
The best recipes for each generation can be seen in table \ref{tab:emma-Gb}. 
The calcinatino heating $v_{cal}$ rate has been predicted perfectly 
\td{even though $v_{cal}$ doesn't appear in the prediction function, how is this possible?}
The number of layers $\lambda$ on the other hand was predicted poorly 
even though the conversion factor wsa 1 and the prediction function dependent on $\lambda$.

@@

\begin{figure}
    \centering
    \begin{subfigure}{.45\textwidth}
        \includegraphics[width=.8\textwidth]{Pics/stats/gen-G.png}
        \caption{emma G gen } \label{fig:emma-G-gen}
    \end{subfigure}
    \begin{subfigure}{.45\textwidth}
        \includegraphics[width=.8\textwidth]{Pics/stats/gen-phd.png}
        \caption{emma phd gen} \label{fig:emma-phd-gen}
    \end{subfigure}
    \caption{emma gen} \label{fig:emma-gen}
\end{figure}

In figure \ref{fig:emma-gen} we can see the two main optimizables at each generation
for each particle.
It shows a clear trend which indicates that the optimization worked even though 
the predicted function and the chosen samples where not exactly as expected. 
This might be due to the high error of samples.

\begin{table}[h]
	\centering
    \caption{Global best per generation}
	\label{tab:emma-Gb}
	\begin{tabular}{cccccccc}
        \hline\hline
    generation  &enr &conc &layr &vDOC &TDOC &vCal &TCal\\
        \hline
     1   &1       &2    &4   &10   &40  &120  &300\\
     2   &5       &2    &6   &10   &40  &120  &300\\
     3   &2947    &4    &6   &16   &80 &1080  &300\\
     4   &2405    &2    &6   &10   &40 &1080  &300\\
     5   &13      &2   &10   &10   &40  &120  &300\\
    \hline\hline
	\end{tabular}
\begin{tabular}{cccccc}
    \hline\hline
enr     &1st gen     &2nd gen        &3rd gen        &4th gen        &5th gen\\
    \hline
1       &1.214185    &       &       &       &38.7962       \\
5       &       &4.196626       &       &       &25.47335       \\
2947    &       &       &10.9594    &       &10.9594       \\
2405    &       &       &       &20.04962   &25.47335       \\
13      &       &       &       &       &24.87178   \\
    \hline\hline
\end{tabular}
\end{table}

%\iffalse
%\fi

%\iffalse
\begin{figure}
\centering
\includegraphics[width=.6\textwidth]{Pics/stats/G-t.png}
    \caption{conductivity G [a.u.] against sample number (is this even correct?)}
    \label{fig:G-t}
\end{figure}

\td{TODO: check if the sorted correctly? Make generation graph with boxplot }
\td{TODO: visualize} how the population moved across the space (with parallel coordinates? or see page 121)
\url{https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation}
%\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{what is best}
\begin{align}
    G &=      -19 + 0.28 * TCal  - 0.022 * layr*TCal  +  0.16 * h(layr-6)*TDOC \\
    \rho &=  -0.87 + 0.0047 * TCal  - 0.00036 * layr*TCal  +  0.0024 * h(layr-6)*TDOC \\
    \lambda &=  6.8 - 0.014 * TCal  + 0.0018 * layr*TCal  + 0.0060 * h(layr-6)*TDOC \\
    v_{cal} &= 29 - 0.052 * TCal  + 0.0011 * layr*TCal  -  0.011 * h(layr-6)*TDOC 
    \label{eq:emma}
\end{align}
%what was the best result? For each particle there is best and global best. 
https://stackoverflow.com/questions/30228281/gnuplot-parallel-coordinates-axes-plot-key-annotation

@@
